IFC Inside: A General Approach to Retrofitting Languages with Dynamic Information Flow Control

### 2014-07-07 paper/real.tex
new approach, wip

In the introduction, we stated that the original motivation behind
developing this embedding was in order to formally specify a
coarse-grained information flow control language for JavaScript.
%
In Section~\ref{sec:retrofit}, however, we used only a simplified
language as an example target language.
%
In this section, we consider the application of our embedding to
JavaScript and two other real world target languages, C and Haskell.
%
Our goal is to show the flexibility of the embedding in settings with
vastly different features and properties, as well as discuss the
semantic gap that must be overcome in some cases to apply our formalism
to other systems.
%
Two of the systems we describe have been implemented: the Haskell
system~\cite{lio} and the SWAPI~\cite{swapi} system; we leave the
implementation of the IFC system for C to future work.

@@

JavaScript (JS), as specified by ECMAScript~\cite{ecma}, does not have any
built-in functionality for I/O. Capabilities such as the ability to
mutate the DOM and read user input are APIs defined on top of the ECMAScript
specification.
%
Consequently, and in contrast to our C and Haskell embeddings---for
which we must eliminate external effects---the embedding for JS is
trivial.

Since this implementation approach relies on multiple runtimes of the
language, sending arbitrary objects between tasks can result in
unexpected behavior, e.g., when the object contains references.
%
As discussed in Section~\ref{sec:concrete}, we need to restrict |send|
to expressions that can be marshalled as strings, i.e., structurally
clonable objects.
%
In our formalization, this amounts to restricting the IFC language rule
for |send| such that only strings can be shared:
%{
\newcommand{\str}{"string"}
%format tOf (e) = "\texttt{typeOf}("e")\texttt{ === \str}"
%format ttrue = "\texttt{true}"
\begin{mathpar}
\inferrule[JS-send]
{
|il canFlowTo il'|\\
|iS(id') = Q|\\
|iS' = iS [ mapsto id' (il', id,  iv) , Q ]|\\
|ie = IT te|\\
|conf tS (tOf te) -> conf tS ttrue|
}
{|
iconf iS (fullconf id il tS (iniEi (send id' il' iv)), ldots)
.->
iS'; sched S (fullconf id il tS (iniEi unit), ldots)
|}
\end{mathpar}
%}
We remark that this is similar to the existing
\texttt{postMessage} API used for iframe and worker
communications~\cite{webworkers}.
%
Thus, the SWAPI implementation provides an IFC version of
\texttt{postMessage}, defined in terms of |send|, that additionally
takes a label argument.

>>>>

In the introduction, we stated that the original motivation behind
developing this embedding was in order to formally specify a
coarse-grained information flow control language for JavaScript.
%
In Section~\ref{sec:retrofit}, however, we used only a simplified
language as an example target language.
%
In this section, we consider the application of our embedding to
JavaScript, and two other real world target languages, Haskell, and C.
%
Our goal is to show the flexibility of the embedding in settings with
vastly different features and properties, as well as discuss the
semantic gap that must be overcome in some cases to apply our formalism
to other systems.
%
%% Two of the systems we describe have been implemented: the Haskell
%% system~\cite{lio} and the SWAPI~\cite{swapi} system; we leave the
%% implementation of the IFC system for C to future work.

An interesting aspect of JavaScript, as specified by
ECMAScript~\cite{ecma}, is that it does not have any built-in
functionality for I/O.
%
(We denote this language as |targetLangJS|.)
%
Instead, when embedding a JavaScript engine, browser layout engines,
such as Gecko, and server-side platforms, such as Node.js, expose APIs
such as the DOM and filesystem as part of the runtime system.
%
In a similar manner, we can directly implement the embedded language
|specLangJS roundrobinf| by exposing (only) our IFC primitives as part
of the runtime and running multiple instances of the JavaScript VM in
separate OS-level threads.\footnote{
  We, indeed, do this for the Gecko implementation when considering
  Web Workers that run operate OS threads.
}
%
Unfortunately, this becomes very costly when an application relies on
many tasks.
%
(Consider, for instance, a server-side web application that wishes to
create a new task for each HTTP request.)

This issue of performance and JavaScript isolation is not unique to
our work. 
%
In particular, browser layout engines rely on the isolation of content
from different origins (e.g., two iframes of different origins) to
implement the \emph{same-origin policy}.
%
Since creating an OS thread for each iframe is expensive, both V8 and
SpiderMonkey provide a means for running JavaScript code in isolation,
on disjoint sub-heaps of the same OS thread.
%
In V8 this unit of isolation is called a \emph{context}~\tocite{}, in
SpiderMonkey, it called a \emph{compartment}~\tocite{}.
%
(We will use these terms and ``task'' interchangeably.)
%
Each context/compartment is associated with a global object, which
implements the JavaScript standard library (e.g., \verb|Object|,
\verb|Array|, etc.).
%
It is this global object that is extended with feature such as the
DOM and filesystem.

\Red{HERE}

Since this implementation approach relies on multiple runtimes of the
language, sending arbitrary objects between tasks can result in
unexpected behavior, e.g., when the object contains references.
%
As discussed in Section~\ref{sec:concrete}, we need to restrict |send|
to expressions that can be marshalled as strings, i.e., structurally
clonable objects.
%
In our formalization, this amounts to restricting the IFC language rule
for |send| such that only strings can be shared:
%{
\newcommand{\str}{"string"}
%format tOf (e) = "\texttt{typeOf}("e")\texttt{ === \str}"
%format ttrue = "\texttt{true}"
\begin{mathpar}
\inferrule[JS-send]
{
|il canFlowTo il'|\\
|iS(id') = Q|\\
|iS' = iS [ mapsto id' (il', id,  iv) , Q ]|\\
|ie = IT te|\\
|conf tS (tOf te) -> conf tS ttrue|
}
{|
iconf iS (fullconf id il tS (iniEi (send id' il' iv)), ldots)
.->
iS'; sched step (fullconf id il tS (iniEi unit), ldots)
|}
\end{mathpar}
%}
We remark that this is similar to the existing
\texttt{postMessage} API used for iframe and worker
communications~\cite{webworkers}.
%
Thus, the SWAPI implementation provides an IFC version of
\texttt{postMessage}, defined in terms of |send|, that additionally
takes a label argument.

@@
